---
title: "Weekly Fantasy Update - 2021"
author: "Jacob Bellairs & Brad Roman"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: true
---
<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r more setup, include=FALSE}
library(tidyverse)
library(ggrepel)
library(ggimage)
library(nflfastR)
library(nflreadr)
library(glue)
library(gt)
library(DT)
# remotes::install_github("jthomasmock/gtExtras")
library(gtExtras)

setwd('C:/Users/bradr/Python/fantasy_football/yahoo')
```

```{r data, include=FALSE, warning=FALSE}
current_season = 2021
current_week = 14
league_size = 10

fastr_player_stats <- nflfastR::load_player_stats()
fastr_rosters <- nflfastR::fast_scraper_roster(current_season)
draft_picks <- read_csv(glue('output/{current_season}_draft_picks.csv'))
player_week_points <- read_csv(glue('output/{current_season}_player_week_points.csv'))
player_season_points <- read_csv(glue('output/{current_season}_player_season_points.csv'))
roster_week <- read_csv(glue('output/{current_season}_roster_week.csv')) %>% mutate(player_key = as.character(player_key))
teams <- read_csv(glue('output/{current_season}_teams.csv'))
player_info <- read_csv(glue('output/{current_season}_player_draft_info.csv'))
transactions <- read_csv(glue('output/{current_season}_transactions.csv'))
weekly_scoreboard <- read_csv(glue('output/{current_season}_current_scoreboard.csv'))
projected_points <- read_csv(glue('output/{current_season}_week{current_week}_projected_points.csv'))
bellairs_rankings <- read_csv(glue('output/{current_season}_bellairs_rankings.csv'))
rookie_ids <- nflreadr::load_ff_playerids() %>% 
  mutate(other_yahoo_id = as.double(yahoo_id),
         yahoo_id = as.double(yahoo_id)) %>% 
  select(name, yahoo_id, position, gsis_id)
source("player_weekly_season_points.R")
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
# cleaning up the data
projected_points <- projected_points %>% 
  left_join(teams, c('team_id')) %>% 
  mutate(winner = ifelse(winner_team_key == team_key, 1, 0),
         points_above_proj = total_points - projected_points) 

proj_points_join <- projected_points %>% 
  group_by(team_id) %>% 
  summarise(sum_projected_points = sum(projected_points))

streak_df <-  projected_points %>% 
  mutate(week = as.numeric(week)) %>% 
  arrange(week) %>% 
  group_by(team_id) %>% 
  summarise(outcomes = list(winner), .groups = 'drop')

expected_wins <- projected_points %>% 
  group_by(week) %>% 
  mutate(rank = rank(desc(total_points))) %>% 
  ungroup() %>% 
  group_by(team_id) %>%
  summarise(exp_wins = round(sum((league_size - rank) / (league_size - 1)), 2)) %>% 
  select(team_id, exp_wins)

keepers <- draft_picks %>% 
  filter((player_key %in% c(30423,31002,30199,32685)) | (round >= 8)) %>%
  anti_join(transactions %>% 
              mutate(dropped_player_id = case_when(type == 'add/drop' ~ player_id_2,
                                                   type == 'drop'     ~ player_id_1)) %>% 
              select(dropped_player_id) %>% 
              distinct(), 
            by = c('player_key' = 'dropped_player_id')) %>% 
  left_join(player_info, 
            by = c('player_key')) %>% 
  left_join(teams %>% mutate(team_id = ifelse(team_id == 10, 0, team_id)),
            by = c('team_key' = 'team_id')) %>% 
  select(team_name, full_name = name, round) %>% 
  arrange(team_name, round, full_name)

```

```{r echo=FALSE,message=FALSE,warning=FALSE}
# roster efficiency / points left on bench
# treating Cordarelle Patterson as an RB
ideal_minus_flex <- roster_week %>%
  # mutate(position = ifelse(position == 'WR,RB','RB',position)) %>% 
  mutate(position = case_when(
    (full_name == "Cordarrelle Patterson") & (team_id == 2) ~ 'RB',
    (full_name == "Cordarrelle Patterson") & (team_id == 3) ~ 'WR',
    TRUE ~ position
  )) %>% 
  group_by(team_id, week, position) %>%
  mutate(pos_rank = rank(desc(fantasy_points), player_key, ties.method = "first"),
         ideal_player_flag = case_when(
           position == 'QB' & pos_rank == 1 ~ 1,
           position == 'RB' & pos_rank <= 2 ~ 1,
           position == 'WR' & pos_rank <= 3 ~ 1,
           position == 'TE' & pos_rank == 1 ~ 1,
           position == 'DEF' & pos_rank == 1 ~ 1,
           position == 'K' & pos_rank == 1 ~ 1,
           TRUE ~ 0
         )) %>%
  ungroup()

ideal_flex <- ideal_minus_flex %>%
  filter(ideal_player_flag == 0,
         position %in% c('RB','WR','TE')) %>% 
  group_by(team_id, week) %>% 
  mutate(flex_rank = rank(desc(fantasy_points), player_key, ties.method = "first")) %>% 
  filter(flex_rank == 1) %>% 
  select(player_key, flex_rank)

ideal_lineup <- ideal_minus_flex %>% 
  left_join(ideal_flex, c('player_key','team_id','week')) %>% 
  mutate(ideal_player_flag = ifelse(ideal_player_flag == 0, flex_rank, ideal_player_flag)) 

team_week_ideal_lineup <- ideal_lineup %>% 
  ungroup() %>%
  group_by(team_id, week) %>%
  summarise(lineup_points = sum(fantasy_points[lineup_position != 'BN']),
            ideal_points = sum(fantasy_points[!is.na(ideal_player_flag)]),
            lineup_efficiency = round(lineup_points / ideal_points, 3),
            points_left_on_bench = ideal_points - lineup_points) %>% 
  arrange(week)

team_season_ideal_lineup <- team_week_ideal_lineup %>% 
  group_by(team_id) %>% 
  mutate(lw_plob = ifelse(week == current_week, points_left_on_bench, 0)) %>% 
  summarise(lineup_points = sum(lineup_points),
            ideal_points = sum(ideal_points),
            # efficiency_list = list(na.omit(lineup_efficiency)),
            lineup_efficiency = round(lineup_points / ideal_points, 3),
            points_left_on_bench = sum(points_left_on_bench),
            last_week_plob = sum(lw_plob)
            )
  
```

<center> <h2>**DyNASTY Power Rankings – The Last Ranking**</h2> </center>
#### It’s the final week of Power Rankings before playoffs, which means things will change slightly. We will include what needs to be done in order to make it for the few teams jostling for the last spot. Time to see where you stand before playoffs begin

1.	**Spencer’s Swag Team (Spencer)**
Spencer’s hot streak remains in play this week, as he easily took Doug’s squad in W13, and he did so without his WR1. The usual suspects led the charge, with Kyler Murray logging 4 TDs in his return to action. His day wasn’t necessarily “stat stuffing” from the pocket, as he only threw the ball 15 times, but he added 10 rushes and scored 2 from each option. His running day provides a huge sigh of relief and shows that Murray is back to 100% after that sprained ankle. JT was the other “main” scorer (Spencer had pretty much everyone in double digits), notching a 24 pt day thanks to 143 yards and 2 TDs on the ground. The next 2 big scorers? Josh Jacobs who has posted 2 straight big games, and Rob Gronkowski who is a top 5 TE since his return to the field after taking some time off to do USAA commercials. Spencer remains the hottest, and scariest, team heading into the final week, and a win would put him as the 3rd seed, whereas a loss would drop him to 4. 

2.	**Tanking for Thibodeaux (Brad)**
It wasn’t Brad’s best week, but the win secured him either the 1 or 2 spot. His 2 best players paved the way for him. Tom Brady had a great game vs Atlanta, going for 368 yards and 4 TDs on 51 attempts (38 completions). Cooper Kupp also stepped up and got his 1st TD since week 8. His 8 receptions and 129 yards were pretty much the usual for Kupp as he’s solidified himself as the ~~greatest player of all time~~ WR1 for the year. His other WRs also had solid games, with Lockett adding 16 and Mike Evans putting up 14 of his own, and they both could’ve easily gone for more. Evans and Lockett are both getting sizable shares (Lockett may even be WR1 in Seattle) and should be able to help carry Brad through the playoffs. Week 14 should also see the return of Alvin Kamara, and Chase Edmonds could start getting worked back into the lineup so Brad’s team is getting healthy when it matters most. A win this week would guarantee the 1, and likely avoidance of Spencer AND/OR most likely Altevers who has put up 160+ a few times this year… spooky stuff. He’s facing Chris, so Brad is probably the 1 seed.

3.	**My Name’s Not derrick (Mark)**
Don’t look now, but Mark has solidified at LEAST 4th places (at most 3rd) and has been one of the hottest teams in the past few weeks. After a breakout game in week 12 against Pittsburgh, Higgins followed up with an even BETTER performance against the Chargers, going 9/138/1 and has 2 straight 100+ yard games after 0 on the season until now. His big game wasn’t what led Mark’s team though… that would be Georgeothy Kittle. Kittle had 9/181/2 as he BULLIED seattle’s defense. If they had just given George the ball every time, San Fran may have won Wan. 2 unlikely names stepped up for Mark in this one too, with Van Jefferson adding 13 and Devonta Freeman getting 18 as the lead back in Baltimore. Freeman has been a huge boost in the running game so far for Baltimore and, despite tough match-ups coming up, should be a huge help as Mark looks to win some money. If Spencer wins, Mark is 4. If Mark wins and Spencer loses, Mark is 3. If they both win/both lose, Mark has a 99.99% chance of being 4. Mark needs to beat Krishna’s playoff-hopeful squad in order to have a chance at being 3.

4.	**Bengals 16-0 (Altevers)**
Altevers lost, but the Pendulum has (at least temporarily) stopped swinging. Altevers put up 128 points no thanks to Patrick Mahomes (14 points), but lots of thanks to Keenan Allen and Leonard Fournette. Allen had a 20-point game, despite only having 34 receiving yards. Of his 5 catches, 2 were for TDs and one was for a 2-pt conversion which are good enough when you don’t care about his actual yards. Fournette’s points also didn’t come from racking up a ton of yards, but he had 7 receptions and got a receiving TD to help make-up for it. He’s been wildly involved as a receiving back which keeps his fantasy value quite high. I would be remiss if I didn’t call out a kicker each week, and this week Jake Elliott gets the nod. Elliott gave Altevers 14! Points, and has now had games of 12.5, 17, 1 (☹), and 14 in the last 4. Unfortunately he’s on a bye in week 14, but he might just be a must-stache Kicker heading into the post season. His up-and-down season has put Altevers in exactly 5th place entering playoffs, regardless of what happens around him.  

5.	**King of The Hill (Doug)**
Not ideal timing for Doug to take a slide in the polls, but that’s what happens when you have 100 points and 97 points in back-to-back weeks and lose your RB1. Doug’s cold streak game to a peak on Monday night, with Josh Allen struggling mightily (because of the weather) against the once again powerhouse that is Bill Belichick’s Patriots. He went 15/30 for 145 yards (because of the weather) but did manage to add 40 yards on the ground (because wind was 30 mph and gusts of 50+ mph). Allen will get sunnier days in Tampa next week to bounce back. Doug also was the recipient of an early injury to Adam Thielen, who only managed 1 catch for 0 yards before spraining his ankle. LASTLY, Tyreek Hill had a down game again, but will likely rebound fine as the Chiefs rely heavily on Hill and Travis Kelce. If the Chiefs want to win, Hill will be a factor. Those three things cost Doug, but honestly his team looked GOOD otherwise. Chris Godwin had a franchise record day, catching 15 crisp spirals from Tom Brady, turning them into 143 yards. He had 20+ points without a TD… SHEEESH. Sony Michel also filled in exceptionally well as Henderson took a bit of a backseat as he works through an injury. Sony had 121 yards and a TD on the ground in this one. Doug is locked in at either the 1 or 2 seed, but similar to Mark’s situation, will only get the 1 if he wins and Brad loses. It’s likely Doug starts the playoff as the #2 seed with a bye.

<center> <h4>**HALFTIME**</h4> </center>
*And then there were 2. Alex Miller and Krishna are the 2 teams left in the battle for the 6 seed. Separated by less than a dozen points, Krishna holds the edge. Imagine if I told you that it all comes down to one game where they face each other. That’s not the case since they actually faced off in week 13, but how fricken cool would that have been? Fate was a week off.*

6.	**Lamar Cowbells (Miller)**
Miller remains ahead of Krishna thanks to, you know, beating him over the weekend. The win wasn’t by a large margin (4 points), but it did inch Alex a little closer to claiming the final playoff spot. Alex was NOT helped by the Patriots playing in 30 mile per hour winds, causing Jakobi Meyers to get 0 of Mac Jones 3 targets during the entire fricken game. MAC JONES THREW THE BALL 3 TIMES IN A GAME. Unfortunately Meyers heads into a bye week so can’t redeem himself quite yet. Miller’s big day was from David Montgomery, who is no newcomer to 20+ point games. Montgomery did it all, rushing for 90 yards and a TD on 21 carries, and also catching the ball 8 times for another 50 yards. It was his first big game since returning from injury, and he got pretty banged up, but Miller has Montgomery’s backup on the bench just in case. Elijah Moore also posted a big game for the squad, getting 6/77/1  as the very clear #1 back for the J-E-T-S, Jets Jets Jets. Alex will only be without Meyers in week 14, and it doesn’t matter if he wins or loses, he just needs points. He’s got a few favorable match-ups, but the last time his QB played the Browns… well it was ugly.

7.	**Dak to the Future (Krishna)**
Krishna took a close, noble, heartbreaking loss in week 13, but his record doesn’t matter and he lost by a close enough margin that he’s still the lead horse for the 6th seed in the playoffs despite being previously deemed “having given up”. Krishna’s squad only put up 104 points, and Diontae Johnson/James Conner/Hunter Renfrow provided over half of them. Diontae was the biggest scorer for Krishna, catching the game winning TD to total 8/105/2 for the day and giving the squad 27 points. James Conner’s 18 points came mostly on the ground, but 1 of his 2 receptions got him the TD he needed to boost his day from good to great. Renfrow was without a TD himself, but his 9/102 stat line gave him 15 points and a much-needed big day for his 2nd week in a row. Now time for the bad. Corey Davis is now on the IR and is done for the season. James Robinson has been banged up and had a bad day against the Rams. He faces an equally difficult match-up with the Titans in week 14. Fortunately, Krishna will get Deebo Samuel, Kareem Hunt, and probably Julio Jones back and is projected to be around 120 points this week. Miller is projected at 128… This is gonna be tight as Krishna needs to outscore him by at least 11 points to make the playoffs. 

8.	**Rammed by OBJ (Jacob) **
Jacob moves up for a second straight week, thanks to a huge day in the battle of the Last-ards. His RBs stepped up for the first time all year, with Javonte Williams leading the charge. Williams had 27 points as the only back in Denver, and has really taken the past 2 weeks to prove that he’s a certified baller when he’s given the snaps. It bodes well for him next season. Antonio Gibson had his 3rd big game in 4 games, rushing for 111 yards and adding 7 receptions for 35 yards. Lastly, Miles Sanders became relevant for 1 whole game, thanks to Jalen Hurts being out. He’s back to being irrelevant next week. Outside of them, Jacob’s day was also pretty lackluster. But OBJ DID GET HIS FIRST TD AS A RAM, then did a Call of Duty celebration, so that was cool to see. Jacob would need a miracle to make the playoffs, and he doesn’t deserve that.

9.	**Fly Me to The Mooney (James)**
An untimely bad day has effectively knocked James out of playoff contention, after a few weeks of looking like he may be able to slip into the 6th spot. His 86 team points came largely from his WRs, as they all played well and were his 3 highest scorers. Russell Gage was targeted 12 times and went 11/130. He’s been a huge option for Matt Ryan the past month or so with Calvin Ridley quitting and Kyle Pitts getting 11-man coverages. Michael Pittman and Jaylen Waddle had solid games of their own, both going for 14 points. Pittman received 8 targets on only 22 attempts, and is the only Colts WR worth a damn according to Carson Wentz, which bodes well for him(although they’re on a bye in w14 sooo not helpful). Waddle has honestly had a quiet, good season and had 9/90 before leaving the game in the 4th quarter due to cramps. Outside of his WRs, James didn’t get much love. Wentz was James’ QB, and he barely threw the ball, and why would he? They have JT. Boston Scott didn’t even play, so that’s 0 points. And Dalton Knox may as well not have, as he only had 2.4 points. It’s likely James doesn’t make the playoffs, but stranger things have happened. He **ONLY** needs to outscore Miller + Krishna both by 30 points.

10.	**The Lions Suck and I’m Sad (Chris)**
Started at the bottom now he’s back. Chris heads into the last week exactly where he started, DFL. It was a very close game between the two worst teams in the league, who actually combined for a surprisingly decent number of points. Chris had huge games from his Vikings. Justin Jefferson (11/182/1) gave Chris 30, and Alexander Mattison added 20 of his own with Dalvin Cook out for the afternoon. Chris got another 24 from Matt Stafford as he surgically picked apart the Jags in the second half, going for nearly 300 yards and exactly 3 TDs. Unfortunately, outside of those 3, there wasn’t much to write home about. Tyler Boyd had a decent day, but Christian Kirk had less than a point, and Chris’ other 2 RBs (not Alexander), combined for 15. Chris didn’t have many options on the bench, so getting this level of productivity from his squad was a nice surprise. Chris is eliminated from the playoffs unless he puts up around 300 points.

***
<center> <h2>**The Bellairs DyNASTY Power Ranking Over Time**</h2> </center>
```{r echo=FALSE,message=FALSE,warning=FALSE, fig.align='center'}
bellairs_rankings %>% 
  left_join(teams %>% select(team_id, team_logo), by = 'team_id') %>% 
  mutate(week_num = as.numeric(week_num)) %>% 
  ggplot() +
  geom_line(aes(x = week_num, y = ranking, color = team_name), show.legend = FALSE) +
  scale_y_continuous(trans = "reverse", breaks = unique(bellairs_rankings$ranking)) +
  scale_x_continuous(breaks = unique(bellairs_rankings$week_num)) + 
  ggimage::geom_image(aes(x = week_num, y = ranking, image = team_logo), size = 0.05, asp = 16 / 9) +
  xlab("Week Number") +
  ylab("Weekly Ranking") +
  theme_classic()
```

***

<center> <h2>**Standings Table**</h2> </center>
*This year we'll be expanding the weekly report with some hard cutting, data-driven metrics of your team. How good are you at setting your lineup? Does Yahoo have accurate projections? Are you doing well because of a good team or favorable schedule? Do you keep your PLOB under control? These are some questions that we hope to answer throughout the season.*

```{r echo=FALSE,message=FALSE,warning=FALSE}
top_records <-  weekly_scoreboard %>% 
  arrange(-win_pct, -points_for) %>% 
  mutate(record_rank = row_number()) %>% 
  select(team_name, win_pct, record_rank, points_for) %>% 
  ungroup()

wildcard <- top_records %>% 
  filter(record_rank >= 5) %>% 
  arrange(-points_for) %>% 
  mutate(points_rank = row_number() + 4) %>% 
  select(team_name, playoff_seed = points_rank)

playoff_seeds <- top_records %>% 
  filter(record_rank <= 4) %>% 
  select(team_name, playoff_seed = record_rank) %>% 
  union(wildcard)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
weekly_scoreboard %>%
  left_join(proj_points_join, 'team_id') %>% 
  left_join(streak_df, 'team_id') %>%
  left_join(expected_wins, 'team_id') %>% 
  left_join(team_season_ideal_lineup, 'team_id') %>% 
  left_join(playoff_seeds, 'team_name') %>% 
  arrange(desc(win_pct), desc(points_for)) %>% 
  mutate(record = paste0(wins, '-', losses, '-', ties),
         pae = points_for - sum_projected_points
         ) %>%
  select(logo = team_logo,
         `Team Name` = team_name,
         Record = record,
         `Win Pct` = win_pct,
         `Expected Wins` = exp_wins,
         Streak = outcomes,
         `Points For` = points_for,
         `Points Against` = points_against,
         `Projected Points For` = sum_projected_points,
         # `Points Above Expectaton` = pae,
         `Ideal Lineup Points` = ideal_points,
         `Lineup Efficiency` = lineup_efficiency,
         `PLOB (Points Left on Bench)` = points_left_on_bench,
         `Last Week PLOB` = last_week_plob,
         Moves = moves,
         `Playoff Seed` = playoff_seed
         # Trades = trades
         ) %>%
  gt() %>%
  gt_img_rows(columns = logo) %>%
  gt_plt_winloss(Streak) %>%
  fmt_percent(column = `Lineup Efficiency`, decimals = 1) %>% 
  gt_theme_nytimes() %>%
  tab_header(title = glue("Week {current_week} Standings")) 
```

***

<center> <h2>**Player Rankings Graphs & Table**</h2> </center>

Here's the same old total points chart, but with bye weeks and injuries players will probably shift positions more easily.

```{r echo=FALSE,message=FALSE,warning=FALSE}
draft_ranks <- draft_picks %>%
  left_join(rookie_ids, by = c('player_key' = 'yahoo_id')) %>% 
  filter(position %in% c('RB','WR','TE','QB')) %>%
  group_by(position) %>%
  mutate(draft_rank = rank(pick),
         pos_rank = paste0(position, draft_rank)) %>%
  ungroup %>%
  select(player_key, pick, full_name = name, draft_rank, pos_rank)

# THIS IS FOR WHEN THE ROOKIE IDS GET UPDATED
# draft_ranks <- draft_picks %>%
#   left_join(fastr_rosters, by = c('player_key' = 'yahoo_id')) %>%
#   filter(position %in% c('RB','WR','TE','QB')) %>%
#   group_by(position) %>%
#   mutate(draft_rank = rank(pick),
#          pos_rank = paste0(position, draft_rank)) %>%
#   ungroup %>%
#   select(player_key, pick, full_name, draft_rank, pos_rank)
```

```{r flex_chart, echo=FALSE,fig.align="center"}
# Points in a season ranked
player_season_points %>% 
  distinct() %>% 
  filter(position %in% c('QB','RB','WR','TE')) %>% 
  arrange(-fantasy_points_1) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  filter(rank <= 30) %>%
  ggplot(aes(x = rank, y = fantasy_points_1)) +
  geom_point() +
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) + 
  xlab("Position Rank") +
  ylab("Fantasy Points") +
  labs(title = "QBs & FLEX PLAYERS",
       caption = "Filtered to Top 30 at each position") +
  theme_classic()
```

Here's a points per game chart that should account for byes and injuries.
```{r flex_chart ppg, echo=FALSE,fig.align="center"}
# Points in a season ranked
player_season_points %>% 
  distinct() %>% 
  filter(position %in% c('QB','RB','WR','TE')) %>% 
  arrange(-avg_fantasy_points) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  filter(rank <= 30) %>%
  ggplot(aes(x = rank, y = avg_fantasy_points)) +
  geom_point() +
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) + 
  xlab("Position Rank") +
  ylab("Average Fantasy Points Per Game") +
  labs(title = "QBs & FLEX PLAYERS",
       caption = "Filtered to Top 30 at each position") +
  theme_classic()
```

```{r kicker_chart, echo=FALSE,warning=FALSE,message=FALSE,fig.align="center"}
player_season_points %>% 
  distinct() %>% 
  filter(position %in% c('K')) %>% 
  arrange(-fantasy_points_1) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  filter(rank <= 32) %>%
  ggplot(aes(x = rank, y = fantasy_points_1)) +
  geom_point() +
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) +
  xlab("Rank") +
  ylab("Fantasy Points") +
  labs(title = "Kickers",
       caption = "Filtered to Top 32") +
  theme_classic()
```


```{r defense_chart, echo=FALSE,warning=FALSE,message=FALSE,fig.align="center"}
nfl_logos <- nflreadr::load_teams() %>% 
  select(team_abbr, team_logo_espn)


player_season_points %>% 
  filter(position %in% c('DEF')) %>% 
  left_join(nfl_logos, by = c('player' = 'team_abbr')) %>% 
  arrange(-fantasy_points_1) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  ggplot(aes(x = rank, y = fantasy_points_1)) +
  ggimage::geom_image(aes(image = team_logo_espn), size = 0.05, asp = 16 / 9) + 
  xlab("Rank") +
  ylab("Fantasy Points") +
  labs(title = "Team Defense") +
  theme_classic()
```

```{r include=FALSE}
draft_ranks %>% 
  left_join(player_season_points, by = c("player_key" = "yahoo_id")) %>% 
  ggplot(aes(x = pick, y = fantasy_points_1)) +
  facet_wrap(draft_ranks$position) + 
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) + 
  xlab("Rank") +
  ylab("Fantasy Points") +
  labs(title = "Team Defense") +
  theme_classic()
  
```


***
*QBs and Flex eligible players are listed. The `Keeper Round` is the round drafted this year.*

```{r player_sort_table, echo=FALSE,message=FALSE,warning=FALSE}
### Here's a table of player ranks and stuff
# rookie_ids replacing fastr_rosters
player_week_points %>%
  distinct() %>%
  filter(position %in% c('QB','RB','WR','TE')) %>%
  left_join(rookie_ids %>% select(gsis_id, full_name = name, new_yahoo = yahoo_id),
            by = c('player_id' = 'gsis_id'))  %>%
  group_by(player_id, full_name, yahoo_id = new_yahoo, position) %>%
  summarise(total_fantasy_points = sum(fantasy_points),
            avg_fantasy_points = round(mean(fantasy_points),1),
            med_points = median(fantasy_points)) %>%
  ungroup() %>%
  left_join(draft_ranks, by = 'full_name') %>%
  mutate(player_rank = rank(desc(total_fantasy_points)),
         draft_rank = draft_rank,
         draft_rank_formatted = paste0(position, ifelse(draft_rank < 10,
                                                        formatC(draft_rank, digits = 1, flag = '0'),
                                                        draft_rank))) %>%
  group_by(position) %>%
  mutate(pos_rank = floor(rank(desc(total_fantasy_points))),
         yahoo_id = as.character(yahoo_id),
         curr_vs_draft = ifelse(draft_rank - pos_rank > 0,
                                paste0('+', draft_rank - pos_rank),
                                draft_rank - pos_rank)) %>%
  ungroup() %>%
  arrange(player_rank) %>%
  left_join(roster_week %>%
              filter(week == current_week) %>%
              select(player_key, team_id, week),
            by = c('yahoo_id' = 'player_key')) %>%
  left_join(teams,
            by = c('team_id' = 'team_id')) %>%
  left_join(keepers, 
            by = c('team_name','full_name')) %>% # took out team_name
  select(Player = full_name,
         Position = position,
         `League Team` = team_name,
         `Player Rank` = player_rank,
         `Position Rank` = pos_rank,
         `Fantasy Points` = total_fantasy_points,
         `Average PPG` = avg_fantasy_points,
         `Drafted Rank` = draft_rank_formatted,
         `Position Current vs Drafted Rank` = curr_vs_draft,
         `Keeper Round` = round) %>%
  datatable(rownames = FALSE, filter = 'top')
```

***








