---
title: "Weekly Fantasy Update - 2021"
author: "Jacob Bellairs & Brad Roman"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r more setup, include=FALSE}
library(tidyverse)
library(ggrepel)
library(ggimage)
library(nflfastR)
library(nflreadr)
library(glue)
library(gt)
library(DT)
# remotes::install_github("jthomasmock/gtExtras")
library(gtExtras)

setwd('C:/Users/bradr/Python/fantasy_football/yahoo')
```

```{r data, include=FALSE, warning=FALSE}
current_season = 2021
current_week = 9
league_size = 10

fastr_player_stats <- nflfastR::load_player_stats()
fastr_rosters <- nflfastR::fast_scraper_roster(current_season)
draft_picks <- read_csv(glue('output/{current_season}_draft_picks.csv'))
player_week_points <- read_csv(glue('output/{current_season}_player_week_points.csv'))
player_season_points <- read_csv(glue('output/{current_season}_player_season_points.csv'))
roster_week <- read_csv(glue('output/{current_season}_roster_week.csv')) %>% mutate(player_key = as.character(player_key))
teams <- read_csv(glue('output/{current_season}_teams.csv'))
player_info <- read_csv(glue('output/{current_season}_player_draft_info.csv'))
transactions <- read_csv(glue('output/{current_season}_transactions.csv'))
weekly_scoreboard <- read_csv(glue('output/{current_season}_current_scoreboard.csv'))
projected_points <- read_csv(glue('output/{current_season}_week{current_week}_projected_points.csv'))
bellairs_rankings <- read_csv(glue('output/{current_season}_bellairs_rankings.csv'))
rookie_ids <- nflreadr::load_ff_playerids() %>% 
  mutate(other_yahoo_id = as.double(yahoo_id),
         yahoo_id = as.double(yahoo_id)) %>% 
  select(name, yahoo_id, position, gsis_id)
source("player_weekly_season_points.R")
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
# cleaning up the data
projected_points <- projected_points %>% 
  left_join(teams, c('team_id')) %>% 
  mutate(winner = ifelse(winner_team_key == team_key, 1, 0),
         points_above_proj = total_points - projected_points) 

proj_points_join <- projected_points %>% 
  group_by(team_id) %>% 
  summarise(sum_projected_points = sum(projected_points))

streak_df <-  projected_points %>% 
  group_by(team_id) %>% 
  summarise(outcomes = list(winner), .groups = 'drop')

expected_wins <- projected_points %>% 
  group_by(week) %>% 
  mutate(rank = rank(desc(total_points))) %>% 
  ungroup() %>% 
  group_by(team_id) %>%
  summarise(exp_wins = round(sum((league_size - rank) / (league_size - 1)), 2)) %>% 
  select(team_id, exp_wins)

keepers <- draft_picks %>% 
  filter((player_key %in% c(30423,31002,30199,32685)) | (round >= 8)) %>%
  anti_join(transactions %>% 
              mutate(dropped_player_id = case_when(type == 'add/drop' ~ player_id_2,
                                                   type == 'drop'     ~ player_id_1)) %>% 
              select(dropped_player_id) %>% 
              distinct(), 
            by = c('player_key' = 'dropped_player_id')) %>% 
  left_join(player_info, 
            by = c('player_key')) %>% 
  left_join(teams %>% mutate(team_id = ifelse(team_id == 10, 0, team_id)),
            by = c('team_key' = 'team_id')) %>% 
  select(team_name, full_name = name, round) %>% 
  arrange(team_name, round, full_name)

```

```{r echo=FALSE,message=FALSE,warning=FALSE}
# roster efficiency / points left on bench
# treating Cordarelle Patterson as an RB
ideal_minus_flex <- roster_week %>%
  mutate(position = ifelse(position == 'WR,RB','RB',position)) %>% 
  group_by(team_id, week, position) %>%
  mutate(pos_rank = rank(desc(fantasy_points), player_key, ties.method = "first"),
         ideal_player_flag = case_when(
           position == 'QB' & pos_rank == 1 ~ 1,
           position == 'RB' & pos_rank <= 2 ~ 1,
           position == 'WR' & pos_rank <= 3 ~ 1,
           position == 'TE' & pos_rank == 1 ~ 1,
           position == 'DEF' & pos_rank == 1 ~ 1,
           position == 'K' & pos_rank == 1 ~ 1,
           TRUE ~ 0
         )) %>%
  ungroup()

ideal_flex <- ideal_minus_flex %>%
  filter(ideal_player_flag == 0,
         position %in% c('RB','WR','TE')) %>% 
  group_by(team_id, week) %>% 
  mutate(flex_rank = rank(desc(fantasy_points), player_key, ties.method = "first")) %>% 
  filter(flex_rank == 1) %>% 
  select(player_key, flex_rank)

ideal_lineup <- ideal_minus_flex %>% 
  left_join(ideal_flex, c('player_key','team_id','week')) %>% 
  mutate(ideal_player_flag = ifelse(ideal_player_flag == 0, flex_rank, ideal_player_flag)) 

team_week_ideal_lineup <- ideal_lineup %>% 
  ungroup() %>%
  group_by(team_id, week) %>%
  summarise(lineup_points = sum(fantasy_points[lineup_position != 'BN']),
            ideal_points = sum(fantasy_points[!is.na(ideal_player_flag)]),
            lineup_efficiency = round(lineup_points / ideal_points, 3),
            points_left_on_bench = ideal_points - lineup_points) %>% 
  arrange(week)

team_season_ideal_lineup <- team_week_ideal_lineup %>% 
  group_by(team_id) %>% 
  mutate(lw_plob = ifelse(week == current_week, points_left_on_bench, 0)) %>% 
  summarise(lineup_points = sum(lineup_points),
            ideal_points = sum(ideal_points),
            # efficiency_list = list(na.omit(lineup_efficiency)),
            lineup_efficiency = round(lineup_points / ideal_points, 3),
            points_left_on_bench = sum(points_left_on_bench),
            last_week_plob = sum(lw_plob)
            )
  
```

<center> <h2>**DyNASTY Power Rankings – Week 9**</h2> </center>
#### A new face makes an appearance at the #1 spot thanks to the biggest upset the league has seen this year. Altever’s pendulum swings back. Teams have acquired some big pieces to make the championship push. Adrian Peterson is playing football again. The weather is getting chilly. This is football szn for realz.

1.	**Spencer’s Swag Team**
Spencer breaches the top spot thanks to an enlightened performance from Jonathan Taylor, who bent the Jets over his knee and spanked them for 200 yards and 2 TDs. JT has been an absolute machine this year, especially since week 3, averaging a whopping 24.5 points in the last 6 games. His next highest scorer was recent trade acquisition Cordarelle Patterson, who has simultaneously taken over the backfield AND become a top receiving option with Calvin Ridley’s leave. Otherwise, it turned out to be a pretty good week for Spencer’s other stars to not really show up, since Altevers only managed 75 points. Ja’Marr Chase was held under 50 yards (16 were on the ground, so the dude only had 32 yards receiving on the day) but it was a product from a prettyyyyyy bad day from Joseph Burrow, and that’s bound to happen every now and then. He was targeted 9 times and is CLEARLY the #1 in Cinci. Spencer also had to plug in a QB (Ryan Tannehill) since both Kyler Murray AND Aaron Rodgers were out, but Spencer should get Murray back this week to take on Krishna. Not having Rodgers wrecked Devante Adams day too, as he only had 6 receptions despite being targeted 14 times by Jordan Love. Ja’Marr Chase and Allen Robinson will be on a bye this week, but Spencer should have the firepower on his squad to overcome the potential upset.

2.	**Tanking for Thibodeaux**
Imagine returning to #1 just to lose to one of the bottom 3 teams the next week. Then imagine Brad. Then imagine a Venn diagram that’s actually just 2 circles overlapping completely. Then add the fact the Bills lost to the Jags. Now imagine Brad reading this like “dude shut up and talk about my team”. Brad’s team had a LOT of good players on bye this week, leaving him to play Cole Beasley and Rondale Moore alongside trade acquisition Cooper Kupp. To make matters even worse, Chase Edmonds is likely headed to IR and RB is the one position Brad is NOT deep at. The good news is that Bye weeks only happen once, and he will get Tom Brady, Mike Evans, and Tyler Lockett back. Russell Wilson also just got cleared so Lockett’s value goes right back up to WR1/2 Range almost immediately. Cooper Kupp had a solid day, with 15 points despite not having a TD. His 11 receptions are a season high, and his floor is probably pretty close to the 12-point mark given how much Matt Stafford obsesses over him. Alvin Kamara did get himself a touchdown and over 100 yards on the day despite adding his BFF Mark Ingram to the backfield. He will lose some touches to Ingram, but it’s not going to actually hurt Kamara that much. If anything, the occasional breather might help Kamara stay fresher during the game. Brad will look to recover from all of the upsets against Mark this week.

3.	**King of the Hill**
Doug very narrowly escaped an upset, but thankfully he was playing a pathetic excuse of a manager in week 9. The team skidded (skode?) by with an 87 point outing, with 0 thanks to Josh Allen or Tyreek Hill. It was Allen’s first truly awful game of the year, and it came against Jacksonville which is absolutely hilarious to everyone that isn’t a Bills fan (Sorry Brad). Tyreek Hill is a different story though, as the Chiefs honestly just look like garbage despite getting a win. Tyreek Hill is 100% stuck because the Chiefs O-line isn’t giving Mahomes enough time to let the play develop. Until that gets fixed, Tyreek will bear the brunt of boom/bust weeks which is unfortunate given how good he would be on like 20 other teams. It was also a down week for CMC thanks to a snap count, but the good news is that he looked solid on the touches he did get (which were actually quite a few anyway). The good news for Doug is 1) he got the W anyway. 2) Allen has the Jets this week. 3) Saquon should be back. 4) CMC looked good. All signs point up for Doug’s team still.

4.	**My Name’s not derRick**
BIGGGGG W for Mark against A Milly this week, wracking up 140 points (ima pay you after I write this, which will be before you read this anyway) behind not Derrick but DerJoe Mixon and DerJustin Herbert. Mixon’s big game was his 3rd such performance in 4 games, and he’s averaging like 21 points a game over the last 4. In this one, It was a combination of land and air, notching 64 rushing yards and 2 TDS, plus getting 46 receiving yards on 5 receptions. Mixon heads into a bye week though, so ☹. Herbert’s day was a big bounce back after 2 pretty bad games in a row… gotta love it. He had an 84% completion rate on the day, throwing for 356/2 TDs and he ran in a TD as well like the dog he is. The experts are saying he’s a middle of the road QB next week, but I don’t buy it. I think he’s a top of the road QB unlike that loser in Kansas City. George Kittle also had a massive game in his return to action after being on IR, raking in a TD on 6/101/1 in San Fran’s loss to Arizona. Last but not least, MG3 had a season high rush attempts and had 80 yards and 1 tuddy to round of a solid day. Amari Cooper and AJ Brown struggled this week, as did flex option Boston Scott despite the Eagles running the ball constantly. Mark takes on Brad this week and will need better games from each of those 3 if he wants a chance to win.

5.	**Lamar Cowbells**
A bit of an unlucky go of things for Alex, as he would’ve beaten over half the teams in the league but instead faced the highest scoring team for the week. His points came largely from team namesake, Cowbells Jackson, who had 120 rushing yards on the day. His QB, Lamar Jackson, threw for 260 and 3 TDS, and they needed every single one in the comeback vs Minnesota. Miller’s 2nd highest scorer was his defense as New England didn’t give Carolina ANYTHING except an ass whooping and 3 Interceptions. Outside of those 2, everyone else played below average, with DJ Moore being a part of the Carolina team I just mentioned, and Jakobi Meyers not really being involved in the Patriot’s offense this week. Zeke managed 11 points despite the Cowboys going “oh shit, we need to throw a lot to try to catch-up to the Broncos”, and he heavily out-touched Pollard before it got to that point. David Montgomery finally returned to action and was immediately RB1 again. Montgomery will probably see a LOT of passes come his way with Justin Fields’ under center, so all-in-all nothing really to worry about. Miller had both of his RB1’s back-ups lol, I just noticed that. He plays the league’s lowest scorer from week 9 this week in what should be a cakewalk. 

<center> <h4>**HALFTIME**</h4> </center>
*Moving halftime back to it’s original spot, as Altevers doesn’t deserve to be above the line after barely escaping from being the worst team this week. Speaking of escaping, you should all check out the show prison break if you haven’t seen it before. It starts to get bad at the end, but it’s definitely worth checking out. Use my promo code “escape” for 10% off any jailbreak products at your local Kroger. *

6.	**Bengals 16-0**
Bi-Polar ass team bro. Alex’s last 4 games are: 182, 70, 140, 75. Whoever he plays next (James), he’s gonna put up 200 so just like, know that’s coming apparently. Week 9 was just really bad for everyone that wasn’t Keenen Allen. Patrick Mahomes? Trash this year. Throw him out. Stefon Diggs? Down game, Josh Allen likes him and he gets targets, they just couldn’t find the endzone or really much of anything in this one. Jerry Jeudy? Broncos love him, so expect bigger numbers soon. Aaron Jones? Also amazing, just didn’t get any passes from Jordan (trash) Love. His numbers will bounce back with Rodgers’ return. Darrell Henderson? Rams sucked on Sunday Night and he paid the price. Tyler Higbee? See above. CeeDee Lamb? Targeted 9 times, Dak was bad. Mason Crosby? Drop his ass. Kicker who misses field goals is sort of like having a QB who misses passes (Mahomes; Trash). Screw it, we’re doing the bench too. TJ Hockenson? Great season, bye week. Leonard Fournette? Great season, bye Week. AJ Green? EH. You just have him because he’s an ex-bengal and don’t try convincing me otherwise. Devin Singletary? Fine plug and play for a bye week. Kenny Golladay? I dropped him for a reason (trash). Jeremy McNichols? Not Adrian Peterson or Derrick Henry (therefore, he’s trash). Alex will recover in week 10 because data says so. 

7.	**Dak to the Future**
WHY NOT pull off the hottest upset of the season and kick Brad while he’s down. Krishna dropped the 2nd most points this week and only 2 actual players scored above their projected numbers. James Conner was projected at 8 and said “nah” so he went ahead and put up 38 on San Fran’s head. He had 170 total yards, with 96 yards and 2 tds on the ground and 5/77/1 through the air. He’s logged 11 TDs on the year very quietly, but this level of production was probably boosted a bit by Kyler Murray AND Chase Edmonds being sidelined. Regardless of the reason, he dominated the game. Nyheim Hines also had a very nice game, especially for the No. 2 RB in Indy, notching 108 total yards and a TD in the colts shootout vs the Jets. He only rushed 6 times, but had 74 yards from those runs. Is he elite? No. But at least he is getting some chances and capitalizing when he does. Otherwise, Dak Prescott and Darren Waller had pretty average games as far as points, but Waller’s came on 7/92/0 in his biggest game since week 1. A TD would’ve been nice, but 7 receptions and matching the team high in targets is a healthy win on its own. While Waller had a “good” average game, Dak’s was the opposite. His statline would’ve been atrocious if not for 2 garbage TDs in his return from an injury last week. Diontae Johnson and Deebo Samuel also struggled despite leading their teams in target share and should rebound nicely next week. Kadarius Toney probably won’t, as the Giants head into a bye week and their WR core is starting to slowly return to health. Krishna’s hoping to ride this hot hand another week as he faces off with Power Ranking #1 Spencer in week 10. 

8.	**The Lions Suck and I’m Sad**
Chris managed to narrowly take the W against James in week 9, despite Calvin Ridley quitting on him. His RB1, first round pick, leader, hero, Nick Chubb notched a casual 29 points on 137 rushing yards/2 TDs, but then the fool went and got Covid despite being vaxxed (@Aaron Rodgers Stans, here’s some ammo). Matthew Stafford’s day was pretty bad, despite throwing the ball like 50 fricken times. Mostly because he threw to the other team twice in back-to-back drives (idiot). The Rams are throwing the ball A LOT, which has helped Robert Woods as Stafford continues to basically look between Woods and Kupp only. Woods had 7/98/0, which was his 2nd highest yards and catches this season. Chris’ Miami G-Men (Gesicki, Gaskin), combined for 20 points in a pretty low scoring game vs the Texans. Ironically, 20 points made the points:fan ratio 20:1 for the game, which was pretty cool to see. Chris also has one of the Eagles’ committee backs who he was forced to insert into this weeks lineup. It didn’t really help, but whatever, points! Last but not least, Justin Jefferson had a great Q1 and was pacing for a 200 yard day, but then got essentially ghosted by Kirk after that. He ended with 3/69(nice)/1 thanks to a 1-yard TD in the 4th, but it’s been a weird few weeks for JJ and Kirk and I don’t like it. Hopefully it’ll turn around because we’re absolutely cheering for Jefferson to be an elite WR and Chris could use the win since he won’t be in the playoffs. He faces off with Doug in week 10.

9.	**Fly Me to The Mooney**
10/10 name change, 6/10 performance in week 9. Unfortunately for James, Chris was able to edge him out in this one. Namesake Darnell Mooney had 2 TDs in the 4th, which saved his otherwise boring night. He had 3/41/1 in the air, and his 2nd TD came on a wildcat handoff from David Montgomery. Tim Patrick also had a surprisingly positive evening, leading the bronco receiving core with 4/85/1 before leaving the game with a knee injury in the 4th. It’s pretty unfortunate timing as Jerry Jeudy is just getting back into things, but hopefully Timmy won’t miss much (or any) time. Jalen Waddle also led his team as far as WR’s go, hauling in 8/83/0 as the #1 receiver while DeVante Parker’s out. Waddle’s value in week 10 is in question though as the starting QB is in question for Miami. I honestly don’t even know which is actually better for Waddle – Tua or Brissett, so maybe it doesn’t actually matter that much. Michael Pittman’s night was strong as well, with 5/64/1 despite only being targeted 6 times during a run-heavy day. He’s had an extremely solid 3-game stretch and has another favorable (unless you’re the Bills) match-up against JAX this coming week. Last thing before I go – James won the “who will get Adrian Peterson” sweepstakes, and was able to get points out of him thanks to a late TD. Otherwise he was looking at like, 2 points for the day. Is AP going to be great? Probably not. Do we want James to play him anyway because it’s such a fun story? ABSOLUTELY. What do you have to lose? James plays Altevers in week 10 and Alex just had a bad week, so watch out. 

10.	**I’m getting Kupped**
Bad. Nothing good happening here. Lowest points scored? Check. Michael Thomas out for the season? Check. Miles Sanders and Antonio Gibson being useless? Check. DK Metcalf being a freak of nature? Check. Jacob traded away all 3 of his good players that aren’t keepers in order to get keepers and draft capital for next season. He’s a threat only to himself at this point, as I don’t think it’s even feasible for any of the players on his roster to have a break out game. Honestly, I am writing this last and it feels a little like a waste of time for me to write this and you to read this. If you’re reading this, it’s too late. His leading scorer had 17 points in week 9, and his kicker had 14% of his points. He still almost won doe. If Jacob upsets Alex Miller in week 10, he gets a legitimate team update next week. 

***
<center> <h2>**The Bellairs DyNASTY Power Ranking Over Time**</h2> </center>
```{r echo=FALSE,message=FALSE,warning=FALSE, fig.align='center'}
bellairs_rankings %>% 
  left_join(teams %>% select(team_id, team_logo), by = 'team_id') %>% 
  ggplot() +
  geom_line(aes(x = week_num, y = ranking, color = team_name), show.legend = FALSE) +
  scale_y_continuous(trans = "reverse", breaks = unique(bellairs_rankings$ranking)) +
  scale_x_continuous(breaks = unique(bellairs_rankings$week_num)) + 
  ggimage::geom_image(aes(x = week_num, y = ranking, image = team_logo), size = 0.05, asp = 16 / 9) +
  xlab("Week Number") +
  ylab("Weekly Ranking") +
  theme_classic()
```

***

<center> <h2>**Standings Table**</h2> </center>
*This year we'll be expanding the weekly report with some hard cutting, data-driven metrics of your team. How good are you at setting your lineup? Does Yahoo have accurate projections? Are you doing well because of a good team or favorable schedule? Do you keep your PLOB under control? These are some questions that we hope to answer throughout the season.*

```{r echo=FALSE,message=FALSE,warning=FALSE}
top_records <-  weekly_scoreboard %>% 
  arrange(-win_pct, -points_for) %>% 
  mutate(record_rank = row_number()) %>% 
  select(team_name, win_pct, record_rank, points_for) %>% 
  ungroup()

wildcard <- top_records %>% 
  filter(record_rank >= 5) %>% 
  arrange(-points_for) %>% 
  mutate(points_rank = row_number() + 4) %>% 
  select(team_name, playoff_seed = points_rank)

playoff_seeds <- top_records %>% 
  filter(record_rank <= 4) %>% 
  select(team_name, playoff_seed = record_rank) %>% 
  union(wildcard)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
weekly_scoreboard %>%
  left_join(proj_points_join, 'team_id') %>% 
  left_join(streak_df, 'team_id') %>%
  left_join(expected_wins, 'team_id') %>% 
  left_join(team_season_ideal_lineup, 'team_id') %>% 
  left_join(playoff_seeds, 'team_name') %>% 
  arrange(desc(win_pct), desc(points_for)) %>% 
  mutate(record = paste0(wins, '-', losses, '-', ties),
         pae = points_for - sum_projected_points
         ) %>%
  select(logo = team_logo,
         `Team Name` = team_name,
         Record = record,
         `Win Pct` = win_pct,
         `Expected Wins` = exp_wins,
         Streak = outcomes,
         `Points For` = points_for,
         `Points Against` = points_against,
         `Projected Points For` = sum_projected_points,
         # `Points Above Expectaton` = pae,
         `Ideal Lineup Points` = ideal_points,
         `Lineup Efficiency` = lineup_efficiency,
         `PLOB (Points Left on Bench)` = points_left_on_bench,
         `Last Week PLOB` = last_week_plob,
         Moves = moves,
         `Playoff Seed` = playoff_seed
         # Trades = trades
         ) %>%
  gt() %>%
  gt_img_rows(columns = logo) %>%
  gt_plt_winloss(Streak) %>%
  fmt_percent(column = `Lineup Efficiency`, decimals = 1) %>% 
  gt_theme_nytimes() %>%
  tab_header(title = glue("Week {current_week} Standings")) 
```

***

<center> <h2>**Player Rankings Graphs & Table**</h2> </center>

Here's the same old total points chart, but with bye weeks and injuries players will probably shift positions more easily.

```{r echo=FALSE,message=FALSE,warning=FALSE}
draft_ranks <- draft_picks %>%
  left_join(rookie_ids, by = c('player_key' = 'yahoo_id')) %>% 
  filter(position %in% c('RB','WR','TE','QB')) %>%
  group_by(position) %>%
  mutate(draft_rank = rank(pick),
         pos_rank = paste0(position, draft_rank)) %>%
  ungroup %>%
  select(player_key, pick, full_name = name, draft_rank, pos_rank)

# THIS IS FOR WHEN THE ROOKIE IDS GET UPDATED
# draft_ranks <- draft_picks %>%
#   left_join(fastr_rosters, by = c('player_key' = 'yahoo_id')) %>%
#   filter(position %in% c('RB','WR','TE','QB')) %>%
#   group_by(position) %>%
#   mutate(draft_rank = rank(pick),
#          pos_rank = paste0(position, draft_rank)) %>%
#   ungroup %>%
#   select(player_key, pick, full_name, draft_rank, pos_rank)
```

```{r flex_chart, echo=FALSE,fig.align="center"}
# Points in a season ranked
player_season_points %>% 
  distinct() %>% 
  filter(position %in% c('QB','RB','WR','TE')) %>% 
  arrange(-fantasy_points_1) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  filter(rank <= 30) %>%
  ggplot(aes(x = rank, y = fantasy_points_1)) +
  geom_point() +
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) + 
  xlab("Position Rank") +
  ylab("Fantasy Points") +
  labs(title = "QBs & FLEX PLAYERS",
       caption = "Filtered to Top 30 at each position") +
  theme_classic()
```

Here's a points per game chart that should account for byes and injuries.
```{r flex_chart ppg, echo=FALSE,fig.align="center"}
# Points in a season ranked
player_season_points %>% 
  distinct() %>% 
  filter(position %in% c('QB','RB','WR','TE')) %>% 
  arrange(-avg_fantasy_points) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  filter(rank <= 30) %>%
  ggplot(aes(x = rank, y = avg_fantasy_points)) +
  geom_point() +
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) + 
  xlab("Position Rank") +
  ylab("Average Fantasy Points Per Game") +
  labs(title = "QBs & FLEX PLAYERS",
       caption = "Filtered to Top 30 at each position") +
  theme_classic()
```

```{r kicker_chart, echo=FALSE,warning=FALSE,message=FALSE,fig.align="center"}
player_season_points %>% 
  distinct() %>% 
  filter(position %in% c('K')) %>% 
  arrange(-fantasy_points_1) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  filter(rank <= 32) %>%
  ggplot(aes(x = rank, y = fantasy_points_1)) +
  geom_point() +
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) +
  xlab("Rank") +
  ylab("Fantasy Points") +
  labs(title = "Kickers",
       caption = "Filtered to Top 32") +
  theme_classic()
```


```{r defense_chart, echo=FALSE,warning=FALSE,message=FALSE,fig.align="center"}
nfl_logos <- nflreadr::load_teams() %>% 
  select(team_abbr, team_logo_espn)


player_season_points %>% 
  filter(position %in% c('DEF')) %>% 
  left_join(nfl_logos, by = c('player' = 'team_abbr')) %>% 
  arrange(-fantasy_points_1) %>% 
  group_by(position) %>% 
  mutate(rank = row_number()) %>% 
  ungroup() %>% 
  ggplot(aes(x = rank, y = fantasy_points_1)) +
  ggimage::geom_image(aes(image = team_logo_espn), size = 0.05, asp = 16 / 9) + 
  xlab("Rank") +
  ylab("Fantasy Points") +
  labs(title = "Team Defense") +
  theme_classic()
```

```{r include=FALSE}
draft_ranks %>% 
  left_join(player_season_points, by = c("player_key" = "yahoo_id")) %>% 
  ggplot(aes(x = pick, y = fantasy_points_1)) +
  facet_wrap(draft_ranks$position) + 
  ggimage::geom_image(aes(image = headshot_url), size = 0.05, asp = 16 / 9) + 
  xlab("Rank") +
  ylab("Fantasy Points") +
  labs(title = "Team Defense") +
  theme_classic()
  
```


***
*QBs and Flex eligible players are listed. The `Keeper Round` is the round drafted this year.*

```{r player_sort_table, echo=FALSE,message=FALSE,warning=FALSE}
### Here's a table of player ranks and stuff
# rookie_ids replacing fastr_rosters
player_week_points %>%
  distinct() %>%
  filter(position %in% c('QB','RB','WR','TE')) %>%
  left_join(rookie_ids %>% select(gsis_id, full_name = name, new_yahoo = yahoo_id),
            by = c('player_id' = 'gsis_id'))  %>%
  group_by(player_id, full_name, yahoo_id = new_yahoo, position) %>%
  summarise(total_fantasy_points = sum(fantasy_points),
            avg_fantasy_points = round(mean(fantasy_points),1),
            med_points = median(fantasy_points)) %>%
  ungroup() %>%
  left_join(draft_ranks, by = 'full_name') %>%
  mutate(player_rank = rank(desc(total_fantasy_points)),
         draft_rank = draft_rank,
         draft_rank_formatted = paste0(position, ifelse(draft_rank < 10,
                                                        formatC(draft_rank, digits = 1, flag = '0'),
                                                        draft_rank))) %>%
  group_by(position) %>%
  mutate(pos_rank = floor(rank(desc(total_fantasy_points))),
         yahoo_id = as.character(yahoo_id),
         curr_vs_draft = ifelse(draft_rank - pos_rank > 0,
                                paste0('+', draft_rank - pos_rank),
                                draft_rank - pos_rank)) %>%
  ungroup() %>%
  arrange(player_rank) %>%
  left_join(roster_week %>%
              filter(week == current_week) %>%
              select(player_key, team_id, week),
            by = c('yahoo_id' = 'player_key')) %>%
  left_join(teams,
            by = c('team_id' = 'team_id')) %>%
  left_join(keepers, 
            by = c('team_name','full_name')) %>% 
  select(Player = full_name,
         Position = position,
         `League Team` = team_name,
         `Player Rank` = player_rank,
         `Position Rank` = pos_rank,
         `Fantasy Points` = total_fantasy_points,
         `Average PPG` = avg_fantasy_points,
         `Drafted Rank` = draft_rank_formatted,
         `Position Current vs Drafted Rank` = curr_vs_draft,
         `Keeper Round` = round) %>%
  datatable(rownames = FALSE, filter = 'top')
```

***








